### 2017-09-27 Writing/draft.tex
Abstract ideas

\noindent{\Large \bf Effect of violating character independence on tree topology}
\bigskip

@@

\newpage
\begin{abstract}
blablabla
\end{abstract}

The project implies inferring a total of 2880 phylogenetic trees (40 replicates of 9 data combination scenarios generating 4 trees each; both inferred in Bayesian and under Maximum Parsimony).
The calculations for the project is ongoing since December 2016 a and is now 95.27\% completed (with a current cumulated computational time of around 80 CPU years that generated 3.2 TB of trees).
The pipelines for analysing the data and producing the publishable figures and tables is already implemented and most of the manuscript is already written ()

Overall we found a positive effect of reducing character correlations on recovering the correct topology.
However, this effect is less important for matrices with a small number of taxa (~25) were reducing character correlation was not more effective than randomly drawing characters.
Furthermore, in bigger matrices (~350 taxa), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.

These results suggest that ignoring the problem of character correlation or independence can easily impact topology in phylogenetic analysis.
However, encouragingly, they also suggest that, unless correlation is effectively maximised or minimised, probabilistic methods can easily accommodate for random correlation between characters.

>>>>

\noindent{\Large \bf Effect of discrete morphological character independence on tree topology}
\bigskip

@@

\newpage
\begin{abstract}
- When using discrete morphological characters for building phylogenies, the characters are assumed to be independent.

- However, this assumption is nearly always wrong, simply because of the nature of morphological integration in organisms.

- The dependence between characters can originate from biological features, shared phylogenetic history or errors from the researcher when coding characters.

- Although the two first sources can be investigated by biologists post phylogenetic inference and the third one can be avoided pre inference with good practices, software do not distinguish between any of them.

- In this study, we propose a new metric of raw character difference as a proxy for character (in)dependence.

- Using thorough simulations and this metric, we test the effect of increasing or decreasing character difference on topology with a variable number of taxa and characters under both Bayesian and Maximum Parsimony inference.

- Overall we found a positive effect of reducing character correlations on recovering the correct topology.

- However, this effect is less important for matrices with a small number of taxa (~25) were reducing character correlation was not more effective than randomly drawing characters.

- Furthermore, in bigger matrices (~350 taxa), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.

- These results suggest that ignoring the problem of character correlation or independence can easily impact topology in phylogenetic analysis.

- However, encouragingly, they also suggest that, unless correlation is effectively maximised or minimised, probabilistic methods can easily accommodate for random correlation between characters.

\end{abstract}
